{{< var titll >}}

### 2025-04-10 index.qmd
abc
cont

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
#webr:
#  show-startup-message: true      # Display status of webR initialization
#  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
#  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
#  cell-options:
#    autorun: true
filters:
  - panelize
  - pyodide
---

@@

>>>>

si---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
#webr:
#  show-startup-message: true      # Display status of webR initialization
#  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
#  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
#  cell-options:
#    autorun: true
filters:
  - panelize
  - pyodide
---

@@

**Last time updated: {{< now timestamp >}}**
